Memory-Efficient Mixed-Precision Implementations\\for Robust Explicit Model Predictive Control

### 2019-08-01 emsoft-2019/camera_ready/Error_Analysis.tex
Small modifications.

 		\item analog-to-digital conversion $\varepsilon_{A/D}$: using the quantized output of the analog-to-digital converter $\hat x$ instead of the actual state $x$. We assume $\|x - \hat x\|\le \varepsilon_{A/D}$.
 		\item quantization of region
 		bounds in memory $\varepsilon_{Q}$: using $\hat H_i,\hat K_i$ which are the quantized versions of $H_i,K_i$ with $p$ bits precision. This is related to the boundaries of the regions.

@@

 	Note that the error resulted from using the quantized versions of $F_i,G_i$ is discussed in \autoref{subsec:app_cont_err}.
 	 %We denote to controllers $\kappa(\mathcal H,x)$ and $\kappa(\mathcal{\hat H},\hat)$ to distinguish between the case that fixed point representation is used or not.

@@

 	 	where $\mathcal{\hat R}_i$ is a polyhedral region determined by a set of linear inequalities $\mathcal{\hat R}_i= \{ \hat x\in\mathcal X\,|\, \hat H_i\hat x\leq \hat K_i\}$. Let us also define the sets $\mathcal H := \{H_i,K_i,i=1,2,\ldots, P\}$ and $\mathcal F:=\{F_i,G_i,i=1,2,\ldots, P\}$. Similarly, we define $\hat{\mathcal H}:= \{\hat H_i,\hat K_i,i=1,2,\ldots, P\}$ and $\hat{\mathcal F}:=\{\hat F_i,\hat G_i,i=1,2,\ldots, P\}$. Using the triangle inequality we have:

@@

@@

 	 	where $\kappa(\mathcal H^*,\mathcal F^*,x^*)$ denotes the controller defined over the sets $\mathcal F^*$, $\mathcal H^*$ and the state $x^*$. The second term corresponds to the control approximation error and will be discussed in \autoref{subsec:app_cont_err}.

>>>>

 		\item analog-to-digital conversion $\varepsilon_{A/D}$: 
		the error introduced by using the quantized output of the analog-to-digital converter $\hat x$ instead of the actual state $x$. 
		We assume $\|x - \hat x\|\le \varepsilon_{A/D}$.
 		\item quantization of region bounds in memory $\varepsilon_{Q}$: the error introduced by 
		using the quantized versions $\hat H_i$, $\hat K_i$ of $H_i$, $K_i$ with $p$ bits of precision. 
		This is related to the boundaries of the regions.

@@

 	Note that the error resulting from using the quantized versions of $F_i,G_i$ will be discussed in \autoref{subsec:app_cont_err}.

@@

 	 	where $\mathcal{\hat R}_i$ is a polyhedral region determined by a set of linear inequalities 
$\mathcal{\hat R}_i= \{ \hat x\in\mathcal X\mid \hat H_i\hat x\leq \hat K_i\}$. 
Let us define the sets $\mathcal H := \{H_i,K_i\mid i=1,2,\ldots, P\}$ and $\mathcal F:=\{F_i,G_i \mid i=1,2,\ldots, P\}$. 
Similarly, we define $\hat{\mathcal H}:= \{\hat H_i,\hat K_i\mid i=1,2,\ldots, P\}$ and $\hat{\mathcal F}:=\{\hat F_i,\hat G_i\mid i=1,2,\ldots, P\}$. 
Using the triangle inequality we have:

@@

 	 	\|\le&\|\kappa(\mathcal H,\mathcal F,x)-\kappa(\hat{\mathcal H},\mathcal F,\hat x)\| +\|\kappa(\hat{\mathcal H},\mathcal F,\hat x)-\kappa(\hat{\mathcal H},\hat{\mathcal F},\hat x)\|.

@@

 	 	where $\kappa(\mathcal H^*,\mathcal F^*,x^*)$ denotes the controller defined over the sets $\mathcal F^*$, $\mathcal H^*$ and the state $x^*$. 
	The second term on the right corresponds to the control approximation error and will be discussed in \autoref{subsec:app_cont_err}.
